---
title: "Causal Mediation Analysis for Heterogeneous Effect"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Causal Mediation Analysis for Heterogeneous Effect}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(hetero.mediation)
```

# Binary Mediator and Binary Outcome

## Fit the mediator model using logistic regression
```{r}
model.m.binary <-glm(wave_II_exercise ~ neighbor_poverty*urbanity, data = smoke, weights = weight, family=quasibinomial(link='logit'))
```




## Fit the outcome model using log-linear with percentage of smoke is 33.7%
```{r}
model.y.binary <- glm(ysmoke ~  neighbor_poverty * wave_II_exercise + neighbor_poverty * urbanity + wave_II_exercise * urbanity, data = smoke, weights = weight, family=poisson(link='log'))
```

## Causal Mediation Analysis for Heterogeneous Effect 
```{r}
hetero.mediate(model.m.binary, model.y.binary, treat = 'neighbor_poverty', modifier = 'urbanity', mediator = 'wave_II_exercise', n = 2579, conf.level = 0.95, yreg = 'logistic', mreg = 'logistic')
```

# Continuous Mediator and Binary Outcome

## Fit the mediator model using linear regression
```{r}
model.m.conti <-lm(wave_II_friend_drug ~ neighbor_poverty*urbanity, data = smoke, weights = weight)
```

## Fit the outcome model using logistic regression
```{r}
model.y.binary2 <- glm(ysmoke ~  neighbor_poverty * wave_II_friend_drug + 
                         neighbor_poverty * urbanity + wave_II_friend_drug * urbanity, data = smoke, weights = weight, 
                       family=quasibinomial(link='logit'))
```

## Causal Mediation Analysis for Heterogeneous Effect 
```{r}
hetero.mediate(model.m.conti, model.y.binary2, treat = 'neighbor_poverty', modifier = 'urbanity', 
               mediator = 'wave_II_friend_drug', n = 2579, conf.level = 0.95, yreg = 'logistic', mreg = 'linear')
```


